Learning by Teaching a Robot:\\The Case of Handwriting

### 2015-12-15 main.tex
First lines of a real discussion

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

The four school studies, the experiment at the surgery and the two case-studies
provide a first broad picture of how a robot-based remediation to handwriting
is accepted by the children and practitioners, and what are the outcomes that
can be expected.

In total, more than 80 children have interacted with the system, for a total
duration of more than 38 hours in multiple experimental configurations
(individual interaction \vs pairs \vs groups; at school, in the lab, at a
surgery; short interactions \vs long, repeated interactions; 5 to 8 years old
children).
